mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2023-01-13 rj/mathml.Rmd
context-dependent rendering of mistakes

```{r, results='asis'}
t <- quote(dfrac(omit_right(mean(D) - mu[0L]), s / sqrt(N)))
mathout(t, flags=list(error='highlight'))
```

@@

For this purpose, the functions `mathml()` or `mathjax()` have an optional
argument `flags` which is a list with named elements. In this example, we use
this argument to tell \pkg{mathml} how to render such erroneous
expressions (asis, highlight, fix, or ignore), see Table \@ref(tab:mistakes).

@@

t <- cbind(Operation=op1, 
  "error asis"=asis, highlight=high, fix=fix, ignore=igno)
knitr::kable(t, caption="Highlighting elements of a term",
  row.names=FALSE, escape=FALSE)
```

>>>>

```{r, results='asis'}
t <- quote(dfrac(omit_right(mean(D) - mu[0L]), s / sqrt(N)))
mathout(t, flags=list(error='highlight'))
mathout(t, flags=list(error='fix'))
```

@@

For this purpose, the functions `mathml()` or `mathjax()` have an optional
argument `flags` which is a list with named elements. In this example, we use
this argument to tell \pkg{mathml} how to render such erroneous
expressions using the flag `error` which can be asis, highlight, fix, or ignore.
For more examples, see Table \@ref(tab:mistakes).

@@

t <- cbind(Operation=op1, 
  "error\\ =\\ asis"=asis, highlight=high, fix=fix, ignore=igno)
knitr::kable(t, caption="Highlighting elements of a term",
  row.names=FALSE, escape=FALSE)
```
